Analysing Constraint Grammars with a SAT-solver

### 2016-03-07 paper/lrec/eval_futurework.tex
mention two versions of spanish + ambiguity class constraint generation takes time

@@

However, many of the use cases do not require running the whole
grammar. Testing the interaction between 5--10 rules takes just
seconds, regardless of the language.

>>>>

We include two versions of the Spanish grammar in table~\ref{table:res}: in column 2, we added the lemmas and word forms as described in Section~\ref{sec:realistic_readings}, and in column 3, we just added each word form and lemma as individual readings, allowed to combine with any other reading. \todo{check if true: This did not affect the amount of conflicts detected, but we found some differences in the generated output; examples will be shown later in this section.}

@@

However, many of the use cases do not require running the whole
grammar. Testing the interaction between 5--10 rules takes just
seconds in all languages, if the ambiguity class constraints are not included. 
A downside in the ambiguity classes is that generating them takes a long time, 
and while 5-minute overhead may be acceptable when checking the full grammar,
it is hardly so when analysing just a handful of rules.
